Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-19 cav2017/cav2017.tex
ciao

\begin{abstract}
This work presents a sound and automated approach to synthesise digital feedback control architectures for physical plans represented as linear, time invariant models. 
Models are encompassed by dynamical equations with inputs, evolving over a continuous state space describing the evolution of the physical variables of the system.

\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
Quantisation; 
Fixed-point arithmetics; 
CEGIS; 
safety requirements. 
}
\end{abstract}

>>>>

\begin{abstract}
This work presents a sound and automated approach to synthesise digital feedback control architectures for physical plans represented as linear, time invariant models. 
Models are encompassed by dynamical equations with inputs, evolving over a continuous state space describing the evolution of the physical variables of the system.  
The approach is divided in two main part, brought together by a counter-example guided inductive synthesis (CEGIS) loop, as follows.   
First, we devise a static feedback controller that stabilises the system;  
then, we verify its potential safety by means of either of the following approaches: 
forward reachability analysis via unfolding of the dynamics, or invariance generation;  
if the above step fails, we loop back and invoke a CEGIS call to seek alternative stabilising feedbacks, 
benefitting from the obtained counter-examples to safety. 
[Mention GA and Abstract Acceleration here?] 
The approach is proven sound by accounting for errors due to \ldots 
We test the procedure on a gazillion benchmarks, excruciatingly encoded manually by Iury and Lucas. 
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
Quantisation; 
Fixed-point arithmetics; 
CEGIS; 
safety requirements. 
}
\end{abstract}
